---
title: "p8105_hw3_zh2494"
author: "zhuolun"
date: "10/15/2021"
output: github_document
---

```{r}
library(p8105.datasets)
library(tidyverse)
library(dplyr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 1.0,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1 
```{r}
data("instacart")
summary(instacart)
size_sum(instacart)
structure(instacart)
colnames(instacart)
```
Description:
the dataset include 15 variables and 1,384,617 observations.
the variable are showing below
order_id: order identifier
product_id: product identifier
add_to_cart_order: order in which each product was added to cart
reordered: 1 if this prodcut has been ordered by this user in the past, 0 otherwise
user_id: customer identifier
eval_set: which evaluation set this order belongs in (Note that the data for use in this class is exclusively from the “train” eval_set)
order_number: the order sequence number for this user (1=first, n=nth)
order_dow: the day of the week on which the order was placed
order_hour_of_day: the hour of the day on which the order was placed
days_since_prior_order: days since the last order, capped at 30, NA if order_number=1
product_name: name of the product
aisle_id: aisle identifier
department_id: department identifier
aisle: the name of the aisle
department: the name of the department

##### 1,How many aisles are there, and which aisles are the most items ordered from?
```{r}
instacart %>%
  count(aisle) %>%
  arrange(desc(n))
```

```{r}

instacart %>% 
  group_by(aisle) %>% 
  summarize(n_obs = n()) %>% 
  mutate(
    nobs_ranking = min_rank(desc(n_obs)),
    nobs_ranking = as.integer(nobs_ranking)) %>% 
  filter(nobs_ranking == 1)
```

*comment: they are `134` aisles, the `fresh vegetables aisles` are the most items ordered.* 

##### Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
instacart %>%
  count(aisle) %>%
  filter(n >= 10000) %>% 
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle,n)
  ) %>%  
  ggplot(aes(y = n, x = aisle)) +
  geom_bar(aes(fill = aisle), stat = "identity") +
  coord_flip()
  labs(
    title = "aisles with more than 10000 items ordered",
    x = "the number of items",
    y = "the name of the aisle"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

*comment : The bar diagram above showed the number of items ordered in aisles, which had more than 10000 items ordered.*


##### 3.Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>%
  filter(rank <= 3) %>% 
  arrange(aisle, rank) %>% 
  knitr::kable()
```

*comment : the baking ingredients need the most light brown sugar. Dog food care need Snack Sticks Chicken & Rice Recipe Dog Treats and packaged vegetables fruits need the most Organic Baby Spinach.*

##### Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r}
instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name,order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>%
  mutate(order_dow = recode(order_dow,`0` = "Sunday", `1` = "Monday", `2` = "Tuesday", `3` = "Wednesday", `4` = "Thurday", `5` = "Friday", `6` = "Saturday")) %>%
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  ) %>% 
  knitr::kable()
```

# Problem 2

Load the dataset

```{r}
data("brfss_smart2010")
```

```{r}
Brfss = 
  brfss_smart2010 %>% 
  filter(Topic == "Overall Health") %>%
  filter(Response %in% c("Excellent","Very good","Good","Fair","Poor")) %>%
  mutate(
    Response = forcats::fct_relevel(Response,c("Poor","Fair","Good","Very good","Excellent")),
    Response = as.factor(Response))
Brfss
```

##### In 2002, which states were observed at 7 or more locations? What about in 2010?

```{r}
location_2002 = 
  Brfss %>% 
  filter(Year == 2002) %>% 
  group_by(Locationabbr,Locationdesc) %>%
  summarize(
    n = n(),
  ) %>% 
  count(Locationabbr) %>% 
  filter(n >= 7)


location_2010 =
  Brfss %>% 
  filter(Year == 2010) %>% 
  group_by(Locationabbr,Locationdesc) %>%
  summarize(
    n = n(),
  ) %>% 
  count(Locationabbr) %>% 
  filter(n >= 7)

location_2010
location_2002

```

*comment: the states that were observed at 7 or more locations are`r pull(location_2002,Locationabbr)` in 2002, the states that were observed at 7 or more locations are`r pull(location_2010,Locationabbr)` in 2010*

##### 3. Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r}
Brfss %>%
  filter(Response == "Excellent") %>% 
  group_by(Year, Locationabbr) %>% 
  summarise(
    mean_data_value = mean(Data_value, na.rm = TRUE)
  ) %>% 
  ggplot(aes(x = Year, y = mean_data_value, color = Locationabbr)) + 
  geom_point() + 
  geom_line() +
  theme(legend.position = "right")
```


##### 4. Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

```{r}
two_panel_plot = 
  Brfss %>% 
  filter(Year %in% c(2006,2010),
         Locationabbr == "NY")
ggplot(two_panel_plot, aes(x = Data_value, fill = Response)) +
  geom_density(alpha = .5, adjust = .5, color = "blue") +
  facet_grid(. ~ Year)
```

# Problem 3

##### 1. Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).

```{r}
accel = 
  read_csv("accel_data.csv") %>%
  mutate(
    weekdays = 
          ifelse(day %in%
          c("Monday","Tuesday","Wednesday","Thursday","Friday"),
          "weekday",ifelse(day %in% c("Saturday","Sunday"),"weekend",NA))
    ) %>% 
  select("week","day_id","day","weekdays",everything())
head(accel)
```

##### 2. Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?

```{r}
accel %>% 
  pivot_longer(
    activity.1:activity.1440,
    names_to = "time",
    names_prefix = "activity.",
    values_to = "activity"
  ) %>%
  group_by(day_id, weekdays) %>%
  summarize(everyday_total = sum(activity)) %>%
  knitr::kable()
  
```

```{r}
# to get the trends from the dataset

accel %>% 
  pivot_longer(
    activity.1:activity.1440,
    names_to = "time",
    names_prefix = "activity.",
    values_to = "activity"
  ) %>%
  group_by(day_id, weekdays) %>%
  summarize(everyday_total = sum(activity)) %>%
  ggplot(aes(x = day_id, y = everyday_total, group = weekdays)) +
  geom_point() +
  geom_line(aes(color = weekdays)) +
  labs(title = "plot for total activity counts in a week", 
       x = "day",
       y = "total count")
```

*comment : Trends: The total activity counts in every weekend tended to decrease when time went by.*

##### 3. Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.

```{r}
accel %>% 
  pivot_longer(
    activity.1:activity.1440,
    names_to = "time",
    names_prefix = "activity.",
    values_to = "activity"
  ) %>%
  mutate(time = as.numeric(time)/60) %>%
  ggplot(aes(x = time, y = activity)) + geom_line(aes(color = day, alpha = .5)) +
  scale_x_continuous(
    breaks = c(0, 4, 8, 12, 16, 20, 24),
    labels = c("0", "4", "8", "12", "16", "20", "24"))
```

*Conclusion: the plot above showed that this man tended to have more activity counts around 12:00PM, between 8:00PM and 10:00PM in a day. Activity counts were in low status in the evening between 12:00AM and 4:00AM in a day, with a possible reason that he might be sleeping.*
